### 2020-09-25 mathematics.tex
add codes for diagonalization

\subsection{Matrix diagonalization}
In this section, $\mathbb K=\mathbb{R}$ or $\mathbb{C}$ and $\mathbb U_{\mathbb K}^{n}\subset \mathbb K^{n\times n}$ is the set of the unitary matrices.

@@

@@

\end{document}

>>>>

\subsection{Matrix diagonalization}\label{app:diagonalization}
In this section, $\mathbb K=\mathbb{R}$ or $\mathbb{C}$ and $\mathbb U_{\mathbb K}^{n}\subset \mathbb K^{n\times n}$ is the set of the unitary matrices.

@@

The calculation on Mathematica is straightforward for this convention:
\begin{minted}{wolfram}
{u, d, v} = SingularValueDecomposition[M]
\end{minted}

@@

Sample Mathematica code to calculate $\{D,R\}$ (with ordering, if specified) is:
\begin{minted}{wolfram}
AutonneTakagi[M_, order_ : None] := Module[{v, p, ord, R, D},
  ord = If[order === None, Range[Length[M]], order];
  v = Transpose[SingularValueDecomposition[M][[3]]];
  p = DiagonalMatrix[(#/Abs[#])^(-1/2) & /@ Diagonal[v.M.Transpose[v]]];
  R = ConjugateTranspose[Reverse[p.v][[ord]]];
  D = ConjugateTranspose[R].M.Conjugate[R];
  {D, R} ];
\end{minted}
\end{document}
